plyranges: a grammar for manipulating genomics data

### 2018-02-12 paper.Rmd
higher level headings

@@

@@

@@

and returns

- recasting overlapping/nearest etc as joins

- split-apply-combine strategies (group_by + reduce/summarise/mutate/filter)

- note on the NSE

>>>>

### Core verbs

@@

### Arithimetic

@@

### Overlapping Ranges

@@

The pairing operations, `pair_overlap()`, `pair_nearest()`, `pair_follow()`, 
and `pair_precede()` are similar to the join operation but instead of returning
a Ranges, they pair up the subject and query Ranges objects into a DataFrame,
alongside their metadata columns. This data structure is similar to the _Pairs_
data structure in the _S4Vectors_ package or the BED-PE file format. 
<!--- should also create convience methods for grouping by pairs and pairing up, 
unpairing, would also be useful for alignments too--->

### Non-standard evaluation
